---
title: "ANA 515 assignment 2"
author: "Ariana Horn"
date: '2022-06-18'
output: 
  html_document:
   bootswatch: morph
---

## **Dataset Introduction**

My dataset contains information about different drug uses in different age groups. This data was collected over a survey and containS 17 observations and 28 variables. Unfortunately, there were some values in variables which made the row a character instead of a numeric. I had to change this and lost in the row age 7 observation, because the age was scaled in some parts. It was interesting to see which drugs in different age groups are more and less used.

[^1]: Loading data into R and installing packages. 

```{r setup, include=FALSE}
library(knitr)
library(tidyr)
library(ggplot2)
library(dplyr)
library(tidyverse)
```

```{r, include=TRUE}
#loading data into R 
library("readr")

urlfile="https://raw.githubusercontent.com/fivethirtyeight/data/dcafc374774f45ede5dd9b8c22ff8097b79a243c/drug-use-by-age/drug-use-by-age.csv"
#rename dataset to mydataset 
mydataset<-read_csv(url(urlfile))
```

```{r, echo=TRUE}
#taking a look on 'mydataset' and rename column [2] from 'n' to 'participants'
names(mydataset)[2]<-"participants"
```

```{r, include=TRUE}
#taking a look on what my colums are names and their values 
#looking at the first 8 columns
str(mydataset[1:8])

#loading package tidyverse for any kind of cleaning
library("tidyverse")

#checking on missing values NA/nulls
complete.cases(mydataset)
summary(mydataset)
#I found 7 columns which are characters
#changing columns from character to numeric 
#column 1 8 10 12 16 20 26 characters 

str(mydataset)
mydataset$age<-as.integer(mydataset$age)
mydataset$`cocaine-frequency`<-as.integer(mydataset$`cocaine-frequency`)
mydataset$`crack-frequency`<-as.integer(mydataset$`crack-frequency`)
mydataset$`heroin-frequency`<-as.integer(mydataset$`heroin-frequency`)
mydataset$`inhalant-frequency`<-as.integer(mydataset$`inhalant-frequency`)
mydataset$`oxycontin-frequency`<-as.integer(mydataset$`oxycontin-frequency`)
mydataset$`meth-frequency`<-as.integer(mydataset$`meth-frequency`)

summary(mydataset)

#identify NA's in age and keeping them in a different dataset 
mydatasetNAs<-subset(mydataset,is.na(mydataset$`age`))

#removing NA's rows from age column
mydataset<-mydataset[!is.na(mydataset$age),]
#replacing other NA's to 0 
mydataset[is.na(mydataset)] = 0
summary(mydataset)


#creating a graph of age and marijuana-use
ggplot(mydataset, aes(x=`age`, y=`marijuana-use`)) + geom_col()
#this graph was for my personal information to see the ratio in use and age, most use of marijuana is in the age 18-21 

```

## **The data frame has 7 rows and 6 columns. The names and brief description of the columns are in the table below:**

```{r, include=TRUE}
knitr::kable(head(mydataset[, 1:6]), "simple")
```

```{r, include=TRUE}
alc_marijbyage <- subset(mydataset, select = c(`age`,`alcohol-use`, `marijuana-use`))
summary_new <- summary(alc_marijbyage)
print(summary_new)
```
